\documentclass[main.tex]{subfiles}

%
\begin{document}


\ifsubbuild
\setcounter{section}{2}
\section{Name}
\fi

\begin{parag}{How to use the `parag' environment?}
 \pitemo{This is the first point - about `pitemo'}{
 Every answer is segregated point-wise using `pitemo' command. The first input of `pitemo' command is a key-point answer to the key question. The second input is a descriptive answer which is composed of statements that will make the paragraph in final compilation.}
 %
 \pitemo{This is the second point - format}{Note that all points have a format of writing. Its important that there is no space after we finish the description to ensure proper spacing in the final compilation - see the compilation. Its also important to keep description in the next line for the same reason - see compilation. Also, the comment after each `pitemo' command is not mandatory. \textbf{space here is exaggerated sometimes} }
 %
 \pitemo{This is the third point - controlling compilation}{
 The compilation in debug mode is controlled by the variable `paraen'. Debug mode is disabled if `ifparaentrue' is commented in `global\_preamble.sty'. In debug mode the key-questions and key-point answers are also compiled.}
\end{parag}


\subsection{A Subsection} 
 

\subsection{Another Subsection}

\subsection{Toast to Einstein} 

Here's citations to a paper \cite{einstein}


\ifsubbuild
\printbibliography[segment=\therefsegment, heading=subbibliography] % print chapter bibliography
\fi 


\end{document}